---
title: "group1_HMO"
author: "Mo"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
# Loading Libraries

```{r LoadingLibraries}
if (!require("tidyverse")) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if (!require("ggplotly")) install.packages("plotly", repos = "http://cran.us.r-project.org")
if (!require("ggplot2")) install.packages("ggplot2", repos = "http://cran.us.r-project.org")
if (!require("hrbrthemes")) install.packages("hrbrthemes", repos = "http://cran.us.r-project.org")
if (!require("viridis")) install.packages("viridis", repos = "http://cran.us.r-project.org")
if (!require("kernlab")) install.packages("kernlab", repos = "http://cran.us.r-project.org")
if (!require("rpart")) install.packages("rpart", repos = "http://cran.us.r-project.org")
if (!require("rpart.plot")) install.packages("rpart.plot", repos = "http://cran.us.r-project.org")
if (!require("treemapify")) install.packages("treemapify", repos = "http://cran.us.r-project.org")
if (!require("caret")) install.packages("caret", repos = "http://cran.us.r-project.org")
if (!require("randomForest")) install.packages("randomForest", repos = "http://cran.us.r-project.org")
listOfPackages <- c("tidyverse", "ggplot2", "treemapify", "hexbin", "RColorBrewer", "caret", "plotly","hrbrthemes","viridis","kernlab","rpart","rpart.plot","caret","randomForest")
lapply(listOfPackages, require, character.only = TRUE)
```
# Importing the Data

```{r ReadingData}
df <- read_csv('https://intro-datascience.s3.us-east-2.amazonaws.com/HMO_data.csv')
```
# Understanding the Data

```{r ColumnsInDataset}
colnames(df)
str(df)
```
# Cleaning the Data

*Descriptive Statistics aboutthe data*
```{r}
hmoData <- df
summary(df)
```

*Checking the how many null values we have in out data*
```{r CheckingForNullValues}
sum(is.na(hmoData)) # 158 null values

# Checking each columns for number of nulls
colSums(is.na(hmoData))
# we can see that we have 78 nulls in bmi and 80 nulls in hypertension.

summary(hmoData$bmi)
```

*Filling the missing values by interpolation*
```{r MissingValuesInterpolation-BMI}
#There are null values in bmi and hypertension columns. These columns will be interpolated to fill the missing values.
hmoData$bmi <- imputeTS::na_interpolation(hmoData$bmi)
if(!sum(is.na(hmoData$bmi))) cat("BMI interpolated")

# Since we know that we have many missing values in BMI, lets clean them.
hmoData$hypertension <- imputeTS::na_interpolation(hmoData$hypertension)
if(!sum(is.na(hmoData$hypertension))) cat("Hypertension interpolated")
```

# Visualizing the columns for some EDA
```{r}
hmoData$hypertension <- as.integer(hmoData$hypertension)
hist(hmoData$hypertension, breaks= 2)
```

```{r AgeAnalysis}
#Creating a histogram for the age
hist(hmoData$age, breaks= 20)
#we can observe that the hmoData is non-uniform as there are lot of people with age below 20.
```

```{r AgeAnalysis2}
# Checking for outliers for age
boxplot(hmoData$age) # not clear outliers
```

```{r}
violin_ageBmi <- ggplot(hmoData, aes(age,bmi))
violin_ageBmi<-  violin_ageBmi + geom_violin() + labs(title="Age - BMI distribution",
       subtitle="From the plot, we can see that BMI distribution is maximum around 30\nApproximamtely 42yo's have the least and highest BMI",
       caption="HMO Data",
       x="Age",
       y="BMI")
violin_ageBmi
```

```{r AgeAnalysisVScost}
# checking for a correlation b/w age and cost
hmoData %>% ggplot() +
  aes(x=age, y=cost) +
  geom_point(color= 'blue') +
  geom_smooth(method="lm", se=FALSE) +
  ggtitle("Age vs Cost")
```


```{r BMIAnalysis-Outliers}
# checking for outliers
boxplot(hmoData$bmi) # not clear outliers
```

*Removinfg Outliers*
```{r ComputingQuartilesForIdentifyingOutliers}
quartiles <- quantile(hmoData$bmi, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(hmoData$bmi)
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR
hmoData <- subset(hmoData, hmoData$bmi > Lower & hmoData$bmi <= Upper-1)
```

```{r}
boxplot(hmoData$bmi) # not more outliers
```
```{r BMIAnalysis}
hist(hmoData$bmi, breaks= 20)
```

```{r CorrelationBMIvCost}
# checking for a corelation b/w bmi and cost
hmoData %>% ggplot() +
  aes(x=bmi, y=cost) +
  geom_point(color= 'red') +
  geom_smooth(method="lm", se=FALSE) +
  ggtitle("BMI vs Cost")
```

```{r}
hmoData %>% ggplot() +
  geom_bin2d(mapping = aes(x = bmi, y = cost))

# install.packages("hexbin")
hmoData %>% ggplot() +
  geom_hex(mapping = aes(x = bmi, y = cost))
```


```{r NumberOfChildren}
hist(hmoData$children, breaks=5)
```

*Summarizing the children column*
```{r}
aggr <- hmoData %>% group_by(children) %>% summarise(total_count=n(),
                                                       .groups = 'drop') %>% as.data.frame()
aggr$percent <- (aggr$total_count / nrow(hmoData)) * 100
aggr
```


```{r NumberOfChildren-Outliers}
boxplot(hmoData$children) # no outliers
```

```{r CorrelationNumberOfChildrenvsCost}
# checking for a correlation b/w children and cost
hmoData %>% ggplot() +
  aes(x=children, y=cost) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  ggtitle("Number of children vs Cost")
```

*Analysing the locations*

```{r}
# The following columns can be converted into categorical hmoData.
unique(hmoData$location)
# cost_location <- hmoData %>% group_by(location) %>% summarise(Avg_Cost = mean(cost))
# barplot(cost_location$Avg_Cost)
```

*Analysisng Smoker Trends*

```{r}
cost_smoker <- hmoData %>% group_by(smoker) %>% summarise(Avg_Cost = mean(cost))
barplot(cost_smoker$Avg_Cost)
summary(hmoData$cost[hmoData$smoker =="yes"])
summary(hmoData$cost[hmoData$smoker =="no"])
```

```{r}
hmoData %>%
  ggplot( aes(x=smoker, y=cost, color=smoker)) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter( size=0.4, alpha=0.9) +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    )
    xlab("Smoker Yes/No")
```

*Analysisng Gender Trends*
```{r}
cost_gender <- hmoData %>% group_by(gender) %>% summarise(Avg_Cost = mean(cost))
barplot(cost_gender$Avg_Cost)
summary(hmoData$cost[hmoData$gender =="male"])
summary(hmoData$cost[hmoData$gender =="female"])
```

```{r}
hmoData %>%
  ggplot( aes(x=gender, y=cost, color=gender)) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter( size=0.4, alpha=0.9) +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    )
    xlab("Gender Male/Female")
```


```{r HypertensionPieChart}
pie(table(hmoData$hypertension), labels = c('Without Hypertension', 'With hypertension'))

```

```{r}
aggr <- hmoData %>% group_by(hypertension) %>% summarise(total_count=n(),
                                                       .groups = 'drop') %>% as.data.frame()
aggr$percent <- (aggr$total_count / nrow(hmoData)) * 100
aggr
```

```{r}
sum(hmoData$hypertension > 0 & hmoData$hypertension < 1)
```

*Cost Analysis*

```{r}
summary(hmoData$cost)
```

```{r}
hist(hmoData$cost, breaks = 20)
```

```{r}
boxplot( hmoData$cost, hmoData = hmoData)
```

*Creating Map based on average cost for each location*
```{r}
mapDF <- hmoData %>% group_by(location) %>% summarise(mean(cost))
```

```{r}
us <- map_data("state")
us$state_name <- tolower(us$region)
coord <- data.frame(loc=tolower(mapDF$location),avg_cost=mapDF$`mean(cost)`)
mergedDF <- merge(us,coord, by.x='state_name',by.y='loc')
mergedDF <- mergedDF %>% arrange(order)

```

```{r}

```


```{r}
mergedDF %>% ggplot(aes(map_id= region)) + 
  geom_polygon(color="black",aes(x=long,y=lat, group=group, fill=avg_cost))  +
  expand_limits(x=mergedDF$long, y=mergedDF$lat) +
  coord_map("mercator") +
  ggtitle("Mean Cost for Each Location")
```

*Descriptive Statistics of all columns*
```{r}
summary(hmoData$cost[hmoData$location_type =="Urban"])
summary(hmoData$cost[hmoData$location_type =="Country"])
```

```{r}
summary(hmoData$cost[hmoData$yearly_physical =="No"])
summary(hmoData$cost[hmoData$yearly_physical =="Yes"])
```

```{r}
summary(hmoData$cost[hmoData$exercise =="Active"])
summary(hmoData$cost[hmoData$exercise =="Not-Active"])
```

```{r}
summary(hmoData$cost[hmoData$married =="Married"])
summary(hmoData$cost[hmoData$married =="Not_Married"])
```

```{r}
summary(hmoData$cost[hmoData$gender =="male"])
summary(hmoData$cost[hmoData$gender =="female"])
```
```{r}
unique(hmoData$location)
hmoData$location <- as.factor(hmoData$location)
```

```{r}
hmoData %>%
  # filter(location_typeIsUrban==1) %>%
ggplot( aes(age, cost, color=bmi)) +
  geom_point() +
  theme_bw()
# p <- p +  scale_shape_manual(values = c(0,23))
# ggplotly(p)

```

```{r}
hmoData %>%
  # filter(location_typeIsUrban==1) %>%
ggplot( aes(age, cost, color=smoker)) +
  geom_point() +
  theme_bw()
# p <- p +  scale_shape_manual(values = c(0,23))
# ggplotly(p)
```

```{r}
hmoData %>%
  # filter(location_typeIsUrban==1) %>%
ggplot( aes(age, cost, color=gender)) +
  geom_point() +
  theme_bw()
# p <- p +  scale_shape_manual(values = c(0,23))
# ggplotly(p)
```

#Data Preperation for Modeling
```{r DataPrepForModelTraining}
prepare_data_for_model <- function(df){
  cat("Preparing dataframe for fitting the model....")
  cat("\nRenaming the columns. Current column names are : \n",colnames(df), "\n")
  df <- df[,names(df)!='X']
  df<-
    df %>%
    rename(isSmoker = smoker
           ,gender_isMale = gender
           ,exercise_isActive = exercise
           ,location_typeIsUrban = location_type)
  cat("\nAfter renaming : ",colnames(df))
  # df$isSmoker <- as.integer(df$isSmoker)
  df$married <- as.integer(ifelse(df$married == "Married", 1, 0))
  df$gender_isMale <- as.integer(ifelse(df$gender_isMale == "male", 1, 0))
  df$exercise_isActive <- as.integer(ifelse(df$exercise_isActive == "Active", 1, 0))
  df$location_typeIsUrban <- as.integer(ifelse(df$location_typeIsUrban == "Urban", 1, 0))
  df$isSmoker <- as.integer(ifelse(df$isSmoker == "yes", 1, 0))
  df$yearly_physical <- as.integer(ifelse(df$yearly_physical == "Yes", 1, 0))
  df$Age_Category <- NA
  df <- mutate(df, Age_Category = ifelse(age %in% 0:21, "Young Adults"
                                          ,ifelse(age %in% 21:36, "Adults"
                                          ,ifelse(age %in% 36:51, "Middle Aged Adults", "Old Aged Adults"))))
  df$location <-  as.integer(ifelse(df$location == 'CONNECTICUT', 0,
                                ifelse(df$location == 'RHODE ISLAND', 1,
                                ifelse(df$location == 'MASSACHUSETTS', 2,
                                ifelse(df$location == 'PENNSYLVANIA', 3,
                                ifelse(df$location == 'MARYLAND', 4,
                                ifelse(df$location == 'NEW JERSEY', 5,
                                ifelse(df$location == 'NEW YORK', 6, 'NA'
                                       ))))))))

  df$education_level <-  as.integer(ifelse(df$education_level == 'Bachelor', 0,
                                ifelse(df$education_level == 'Master', 1,
                                ifelse(df$education_level == 'PhD', 2,
                                ifelse(df$education_level == 'No College Degree', 3, 'NA')))))
  return(df)
}
```

```{r}
updatedHMOdata <- prepare_data_for_model(hmoData)
updatedHMOdata
```

```{r}
corr <- cor(updatedHMOdata[, unlist(lapply(updatedHMOdata, is.numeric))], use = "complete.obs")
heatmap(corr, Colv = NA, Rowv = NA)
```

```{r DataPrepForModelTraining-Factorizing}
factorizing_data_for_model <- function(df){
  cat("Preparing dataframe for fitting the model....")
  df$isSmoker<-as.factor(df$isSmoker)
  df$location_typeIsUrban<-as.factor(df$location_typeIsUrban)
  df$exercise_isActive<- as.factor(df$exercise_isActive)
  df$married<-as.factor(df$married)
  df$gender_isMale<-as.factor(df$gender_isMale)
  df$yearly_physical<-as.factor(df$yearly_physical)
  df$hypertension<-as.factor(df$hypertension)
  df$education_level <- as.factor(df$education_level)
  df$Age_Category <- as.factor(df$Age_Category)
  df$location <- as.factor(df$location)
  return(df)
}
```

```{r VariableFactorizatino}
updatedHMOdata<-factorizing_data_for_model(updatedHMOdata)
```

```{r CreateDataPartition}
summary(updatedHMOdata$cost)
str(updatedHMOdata)
```

#Assuming Expensive Criteria
```{r}
quartiles <- quantile(updatedHMOdata$cost, probs=c(.25,.75), na.rm = FALSE)
IQR <- IQR(updatedHMOdata$cost)
Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 
Lower
Upper
quartiles
```

```{r}
updatedHMOdata$expensive <- as.factor(ifelse(updatedHMOdata$cost>quartiles[2],TRUE,FALSE))
updatedHMOdata
```

#Visualizations With Expensive

```{r}
df_age <- updatedHMOdata %>%
  group_by(age, expensive, cost)

plot_e1 <- ggplot(data = df_age, aes(x = age,y = cost, fill = expensive)) + 
  geom_bar(stat='identity') + scale_fill_brewer(palette = 14)
plot_e1 <- plot_e1 + labs(title = 'Expensive by Age', x = 'Ages')
plot_e1
```

```{r}
plot_e2 <- ggplot(data = updatedHMOdata, aes(x = isSmoker, fill = expensive)) + 
  geom_bar() + scale_fill_brewer(palette = 14)
plot_e2 <- plot_e2 + labs(title = 'smoker Vs Non-smoker', x = 'Activity')
plot_e2
```


# Regression Model
```{r Regression Model}
lmOut <- lm(data = updatedHMOdata, cost ~ age + bmi + children + isSmoker + exercise_isActive + hypertension)
summary(lmOut)
```

```{r}
saveRDS(lmOut, "../ist687_hmo/lm_model.rds")
my_lm_model <- readRDS("../ist687_hmo/lm_model.rds")
```

```{r Approach1RegressionPrediction-TrainTestData}
test_file_DF<- data.frame(read_csv('..//HMO_TEST_data_sample.csv'))
test_file_DF <- prepare_data_for_model(test_file_DF)
test_file_DF <- factorizing_data_for_model(test_file_DF)
test_file_DF

test_file_DF_y<- data.frame(read_csv('..//HMO_TEST_data_sample_solution.csv'))
```

```{r Approach1RegressionPrediction-TestData}
costPrediction <- predict(my_lm_model,test_file_DF)
cat(costPrediction)
```

```{r Approach1SVM}
set.seed(1234)
trainSet <- createDataPartition(y = updatedHMOdata$expensive , p= 0.8, list = FALSE)
trainData <- updatedHMOdata[trainSet,]
testData <- updatedHMOdata[-trainSet,]
svmModel <- ksvm(expensive ~ age + bmi + children + isSmoker +  exercise_isActive + hypertension,
                 data = trainData, C = 5, cross =3, prob.model =TRUE)
```

```{r Approach1SVMConfusionMatrix}
test <- testData
predOut <- predict(svmModel, newdata = test, type = "response")
# predOut

confusionMatrix(predOut, testData$expensive)
```

```{r}
# save svm
saveRDS(svmModel, "../ist687_hmo/svm_model.rds")
my_svm_model <- readRDS("../ist687_hmo/svm_model.rds")
```

```{r}
#predict people for which healthcare would be expensive
temp_data <- test_file_DF
temp_data$cost <- costPrediction
predDF <- predict(my_svm_model, newdata = temp_data)
predDF
```

```{r}
#using confusion matrix to check performance of model
test_file_DF_y$expensive
confMatrix<-confusionMatrix(predDF, as.factor(test_file_DF_y$expensive))
plot(confMatrix$table, color = c("cyan", "blue"), conf.level = 0, margin = 1, main = "Confusion Matrix")
confMatrix
```

```{r RPART}
#Decision Tree:
#install.packages("caret") 
library(e1071)
```

```{r}
tree_train_set <- data.frame(
                     children=trainData$children,
                     isSmoker=trainData$isSmoker,
                     exercise_isActive = trainData$exercise_isActive,
                     hypertension =trainData$hypertension,
                     bmi = trainData$bmi,
                     age = trainData$age,
                     expensive =trainData$expensive)

tree_test_set <- data.frame(
                     children=testData$children,
                     isSmoker=testData$isSmoker,
                     exercise_isActive = testData$exercise_isActive,
                     hypertension =testData$hypertension,
                     bmi = testData$bmi,
                     age = testData$age,
                     expensive =testData$expensive)
```


```{r}
trctrl<- trainControl(method="repeatedcv",number=50)
tree_df <- rpart(expensive ~.,data = tree_train_set, method='class')
rpart.plot(tree_df)
summary(tree_df)
# head(tree_train_set)
```

```{r RandomForest}
rf <- randomForest(expensive~., data=tree_train_set, proximity=TRUE)

p1 <- predict(rf, tree_test_set)
confusionMatrix(p1, test$ expensive)

```

```{r}
# SAVE RF Model
saveRDS(rf, "../ist687_hmo/rf_model.rds")
my_rf_model <- readRDS("../ist687_hmo/rf_model.rds")
```


```{r}
# testDF_DT <- testDF[,names(testDF)!= 'age']
# testDF_DT <- testDF_DT[,names(testDF_DT)!= 'cost']
# testDF_DT <- testDF_DT[,names(testDF_DT)!= 'X']
# testDF_DT$location <- as.factor(testDF_DT$location)
p1 <- predict(my_rf_model, test_file_DF)
rf_cm <- confusionMatrix(p1, as.factor(test_file_DF_y$expensive))
rf_cm
plot(rf_cm$table, color = c("cyan", "blue"), conf.level = 0, margin = 1, main = "Confusion Matrix")
```

```{r Apriori}
library(arules)
library(arulesViz)
#df <- matrix(df4)

df_new <- data.frame(ageGroup=updatedHMOdata$Age_Category,
                     children=updatedHMOdata$children,
                     smoker=updatedHMOdata$isSmoker,
                     location=updatedHMOdata$location,
                     location_type=updatedHMOdata$location_typeIsUrban,
                     education_level=updatedHMOdata$education_level,
                     yearly_physical = updatedHMOdata$yearly_physical,
                     exercise = updatedHMOdata$exercise_isActive,
                     married =updatedHMOdata$married,
                     hypertension =updatedHMOdata$hypertension,
                     gender=updatedHMOdata$gender_isMale,
                     expensive =updatedHMOdata$expensive)

df_newer <- as(df_new, 'transactions')

datarules <- apriori(df_newer,
 parameter=list(supp=0, conf=0),
 control=list(verbose=F),
 appearance=list(default="lhs",rhs=("expensive=TRUE")))

```

```{r InspectRules}
inspect(datarules)
inspectDT(datarules)
```
